---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ezlm

<!-- badges: start -->
<!-- badges: end -->

The goal of ezlm is to fit a simple linear regression model, outputting easy-to-read
    results rounded to user's preferred decimal place. A wrapper for lm().

## Installation

The ezlm package is not yet available from [CRAN](https://CRAN.R-project.org). Please download it from this repository using the following R command:

``` r
devtools::install_github("deansn/ezlm")
```

## Example

### Fuel Economy and Horsepower in`mtcars`

As a basic demonstration of the `ezlm()` function, begin by calling the function and inputting the appropriate variables (as described in the documentation above).

Let's say we're interested in the effect of fuel economy on horsepower, and we want to see our results to three decimal places:

```{r example1}
library(ezlm)
ezlm(mtcars, mtcars$mpg, mtcars$hp, 3)
```


### Urban Population and Assaults in `USArrests`

While this function was designed primarily for linear regressions within the `mtcars` dataset, it should work with other datasets, such as `USArrests`. In this example, let's look at the influence of the urban population proportion on the number of assault charges.

```{r example2}
ezlm(USArrests, USArrests$UrbanPop, USArrests$Assault, 2)
```


### Inappropriate Inputs

To force my function to throw one of my custom error messages, we can try to replace one of the numerical parameters with a non-accepted input class:

```{r example3, error = TRUE}
ezlm(mtcars, as.factor(mtcars$mpg), mtcars$hp, 3)
```

As expected, the function throws the custom error message when the IV is defined as a factor variable.

